\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{hyphenat}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}

%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\huge{\textbf{Carlos Henrique Romano}} \vspace{0.1in} \\ \hline \\
\textbf{Date of Birth:} February 11, 1984 & \textbf{Email:} chromano@gmail.com \\
\textbf{Citizenship:} Brazilian & \textbf{Telephone:} +55 16 99163 8180\\
\textbf{Address:} Av Demetrio Mitre, 81 & \textbf{Skype:} chromanoskype \\
    13.564-220 - Sao Carlos - SP - Brazil & \textbf{Website:} http://chromano.me
\end{tabular*}
\vspace{0.2in}

{\large \textbf{About me}}\\
\vspace{0.1in}
%\begin{tabular}{p{16cm}}\\
I am a full stack software developer with 10+ years of experience in end-to-end
application design and development. I'm always looking for challenging projects
where I can apply my extensive knowledge of technologies and methodologies.
My mother tongue is Portuguese, but I am fluent in written English and proficient
in spoken English as well.
\vspace{0.1in}

My primary focus and experience is with WEB development, mostly backend systems.
In addition, I have a great interest and competency in the development of rich
user interfaces using the latest browser and javascript-related technologies, as
well as webscale database and server configuration / optimization.

%\end{tabular}
\vspace{0.2in}

{\large \textbf{Technical Skills}}
%\begin{itemize}
\begin{list}{$\bullet$}{\setlength{\parsep 0.0in}}
  \item \textbf{Development}: I'm a heavy user of Python and C, with experience
in Ruby, PHP and C\#. I'm very comfortable with Object Oriented Programming
principles, design patterns and the Test Driven Development methodology.
I often leverage application frameworks such as Django, Flask and Rails, with
particular expertise in Django.
  \item \textbf{WEB}: HTML, CSS, JS and convenient libraries like jQuery,
Angular, React and Twitter Bootstrap.
  \item \textbf{Databases}: PostgreSQL, MySQL, SQLite and MongoDB. I also have
knowledge of database indexes for optimization of data access.
  \item \textbf{System Administration}: I have extensive experience deploying
and maintaining WEB projects on Linux servers running Apache, as well as
experience with super-efficient lightweight server technologies such
as NginX and uWSGI/gunicorn.
  \item \textbf{Others}: Git, Mercurial and SVN for revision control; Jira,
Trac and Bugzilla for bugs tracking; Gulp, NodeJS for server side scripting
and Celery for long running tasks in the server.

\end{list}
%%\pagebreak
\vspace{0.2in}
{\large \textbf{Professional Experience}}
\begin{itemize}
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    Toptal & 09-2015 to present \\
  \end{tabular*}
  \begin{itemize}
    At Toptal I had the pleasure to work on some interesting projects like
Scriptopia (\textit{scriptopia.co}) and ConsumerAffairs
(\textit{www.consumeraffairs.com}). Even though I was hired initially to
work with the backend of such systems, I always ended up working in the
frontend as well as system administration.
      \end{itemize}
  \end{itemize}
\pagebreak
\begin{itemize}
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    Self-employed & 05-2010 to present \\
  \end{tabular*}
  \begin{itemize}
    Working as consultant of WEB projects. Clients include UkuMi (\textit{www.ukumi.com}),
Magnetic New Media (\textit{www.magneticnewmedia.com}),
QuoteSentinel (\textit{www.quotesentinel.com}) and RocketLease
(\textit{www.rocketlease.com}).  Primary projects:
     \begin{itemize}
         \item Built and configured an EC2 webserver cluster supporting up to
1K requests/sec with concurrency of 100 requests/sec (approx 20M users/mo)
         \item Developed a robust Javascript form-builder using the Backbone.js
framework enabling users to create enrollment forms on demand via a drag and
drop interface (emulating Wufoo's form builder @ \textit{www.wufoo.com})
         \item Optimized the architecture of a quotes monitoring system,
creating a 10X increase in the platform's user concurrency capacity.
         \item Lead developer on a marketing/advertising platform that
enables consumers to create collections of relevant sponsored content, and Brands
to launch targeted display advertising campaigns and remotely manage marketing
assets on partner / consumer sites.
      \end{itemize}
  \end{itemize}
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    Voixtel Telecom & 12-2009 to 05-2010 \\
  \end{tabular*}
    \begin{itemize}
    \item Responsible for the development and integration of a WEB conferencing
module into a VoIP
billing system.
    \end{itemize}
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    Gcomp Tecnologia & 01-2009 to 11-2009 \\
  \end{tabular*}
    \begin{itemize}
    \item Development of a real-time inventory management system using RFID.
The main technologies
used were .NET/C\# and Django/Python.
    \end{itemize}
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    3WT Wireless Web World Tech & 11-2007 to 01-2009 \\
  \end{tabular*}
    \begin{itemize}
    \item Lead developer for a content recommendation system based on
persuasive computing. This
project was developed together with the INdT (Nokia Institute of Technology)
for the Maemo
platform, used by the Nokia Internet Tablets N800 and N810. The technologies
involved in
this project were Python (for both backend and frontend), Twisted (for handling
requests on
the server side), GTK+ and EFL as the graphical toolkits.
    \end{itemize}
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    Gwyddion Intelligent Devices & 06-2007 to 11-2007 \\
  \end{tabular*}
    \begin{itemize}
    \item Maintenance of the GITS telemetry system, using Python and embedded C
for MSP430. I also
developed the WEB interface used for system configuration and data analysis,
which was
written in PHP.
    \end{itemize}
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    MZO Interativa & 01-2007 to 06-2007 \\
  \end{tabular*}
    \begin{itemize}
    \item Developed an event management system (subscriptions management,
payments and reports)
using PHP.
    \end{itemize}
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    Async Open Source & 09/2004 to 12/2006 \\
  \end{tabular*}
    \begin{itemize}
    \item Implemented an open source retail system called Stoq (www.stoq.com.br
) and its underlying
libraries, such as the library responsible for communication with fiscal
printers, check printers,
barcode scanners and electronic scales. I also developed the libraries
responsible for building
and loading graphical interfaces via XML.
    \end{itemize}
\end{itemize}

\end{document}
